\dppTitle

### 2014-06-01 manuscripts/dpp-msbayes/reviews/response.tex

\let\quoteOld\quote
\let\endquoteOld\endquote
% \renewenvironment{quote}{\sffamily\slshape\small\quoteOld}{\endquoteOld}
\renewenvironment{quote}{\sffamily\small\quoteOld}{\endquoteOld}

% \makeatletter
% \renewcommand{\section}{\@startsection{section}{1}{0mm}%
%     {-8pt}%
%     {4pt}%
% {\sffamily\large\itshape}}
% \makeatother

\begin{document}
% \raggedright
\setlength{\parindent}{0in}

I greatly appreciate the helpful comments of the editor and reviewers. In this
document, I provide responses to these comments, including descriptions of the
changes I have made.

\section{Editor's Comments}
\setcounter{commentCounter}{0}
\revcomment{
    Looking at Reviewer 2's list of issues, they appear to relate only to the
    presentation, and Reviewer 2 is not asking for more analysis.  These
    requests for revision are requests for comments, clarifications, and
    statements of caveats to be made by the author.  I think that if these
    requests are attended to then the ms will be improved.
}
\response{
    Reviewer 2's comments were very helpful, and have helped to improve the
    clarity of the manuscript. Below, I address each of Reviewer 2's concerns
    along with the corresponding changes I have made in light of the comments.
}

\revcomment{
    (Concerning Reviewer 2's comment 1.  I did not get the impression that the
    author was criticizing Bayesian foundations, but this Reviewer did, and
    that in itself shows that there is room for misunderstanding.  I suspect
    that the author may feel that the intention of the paragraph is clear
    enough, but perhaps the wording here can be adjusted in the light of this
    reviewer's comment to more clearly say that you are talking about options
    for prior choice, that msBayes has opted for uniform priors, and your
    comments on that.)
}
\response{
    I agree that there was room for misunderstanding given that the context of
    the statements were not made clear. Please see the below for the specific
    edits I have made in response to this helpful comment.
}

\revcomment{
    I would like to ask that in replying to the requests for revision that a
    point-by-point be made to make it easy for us to see what you have done.
}
\response{
    Please see below for my point-by-point revisions. Also, I am attaching a
    PDF of the manuscript with all of the revisions highlighted in color.
}

\section{Reviewer 1's Comments}
\setcounter{commentCounter}{0}
\revcomment{
    In reference to ``Bayesian model-choice method'' in the second paragraph
    of page 2, Reviewer 1 requested a clearer description of the models being
    sampled by such a method.
}
\response{
    I have added the following sentence to this paragraph that provides a
    clearer description of the model sample space and, thanks to Reviewer 1's
    suggestion, provides a smoother transition into the description of the \msb
    model in the following paragraph:
    \begin{quote}
        The sample space of such a model-choice procedure would include all
        models ranging from a single divergence-time parameter (i.e.,
        simultaneous divergence of all co-distributed taxa) to the fully
        generalized model in which each taxon diverged at a unique time.
    \end{quote}
}

@@

\revcomment{
    Reviewer 1 felt the equating of ``biogeographically interesting models''
    with models of shared divergences was unnecessarily subjective.
}
\response{
    I agree. I have removed the use of the model descriptor ``biogeographically
    interesting'' from the manuscript, and have added the following to the
    Conclusions:
    \begin{quote}
        Compared to \msb, the new approach better estimates posterior
        uncertainty, which greatly reduces the chances of incorrectly
        estimating biogeographical scenarios of shared divergence events.  This
        is important, because models of shared divergence events are often of
        particular interest to researchers who employ these methods.
    \end{quote}
    Thanks to Reviewer 1's comment, this is a much clearer description of what
    I was intending to convey with ``biogeographically interesting.''
}

\revcomment{
    Many readers may be generally unaware of several important factors of how
    phylogeographers use msBayes. I'd suggest a review paragraph somewhere in
    the intro that describes your empirical paper and others such that the
    readers have a better concept of why these technical details matter.
}
\response{
    Good point. I have added the following paragraph to the introduction to
    familiarize readers with how \msb has been applied, and the general results
    of such applications.
    \begin{quote}
        \msb has been used to address biogeographical questions in a variety of
        empirical systems. Some examples include (1) whether the rise of the
        Isthmus of Panama caused co-divergence among species of echinoids
        co-distributed across the Pacific and Atlantic sides of the isthmus
        \cite{Hickerson2006}, (2) if an historical seaway across the Baja
        Peninsula caused co-divergence across species of squamates and mammals
        co-distributed both north and south of the putative seaway
        \cite{Leache2007}, (3) if species of gall-wasps and their associated
        parasitoids share divergences across putative glacial refugia
        \cite{Stone2012}, and (4) whether repeated fragmentation of the oceanic
        Islands of the Philippines during Pleistocene sea-level fluctuations
        caused diversification of vertebrate taxa distributed across the
        islands \cite{Oaks2012}.  Such applications of the method often result
        in strong posterior support for co-divergence among all or subsets of
        the taxa investigated (e.g.,
        \cite{Barber2010,Carnaval2009,Chan2011,Hickerson2006,Leache2007,Plouviez2009,Stone2012,Voje2009,Oaks2012}).
    \end{quote}
}

@@

\revcomment{
    In reference to ``I provide the ability to control the richness of the model'' on Page 9,
    Reviewer 1 commented:

    While I appreciate how this flexibility is a selling point to someone who
    is very familiar with this model (such as the author), it might also be
    viewed as an increased difficulty for the average user. Is this to say that
    the 'richness' of the model has to be specified by the user, or can be
    specified? Please clarify.
}
\response{
    To clarify that the user is not required to control the richness of the
    model, I have changed the subsequent sentences to:
    \begin{quote}
        For the \myTheta{} parameters, by default, the model is fully
        generalized to allow each population pair to have three parameters:
        \ancestralTheta{}, \descendantTheta{1}{}, and \descendantTheta{2}{}.
        Furthermore, if an investigator prefers to reduce the number of
        parameters, any model of \myTheta{} parameters nested within this
        general model can also be specified, including the most restricted
        model where the ancestral and descendant populations of each pair share
        a single \myTheta{} parameter.
    \end{quote}
}

\revcomment{
    Reviewer 1 commented that I awkwardly started two consecutive sentences
    with ``However'' on Page 11.
}
\response{
    Thank you for catching this. I have removed ``However'' from the beginning
    of the first sentence, because it was unnecessary.
}

\revcomment{
    Reviewer 1 commented that I was underselling the results in section
    ``Validation analyses: Ordered divergence models'' on Page 16.
}
\response{
    I have expanded this section by including the following sentences:
    \begin{quote}
        This is encouraging, because, as discussed above, estimating unordered
        models of divergence by shuffling the summary statistic vectors
        calculated from the sequence alignments is not valid for most empirical
        datasets.  Given these results, estimation of unordered divergence
        models should be avoided for empirical applications of the method.
    \end{quote}
}

\revcomment{
    Given these caveats, what (in your opinion) is the best usage of this
    approach to phylogeographic analysis?
}
\response{
    This was an important observation by Reviewer 1 that I was listing a lot of
    potential problems with the new method without providing any advice or
    guidance on how to navigate such potential pitfalls and how to best use the
    method. I have added the following paragraph following the discussion of
    caveats:
    \begin{quote}
        Given all of these caveats, I encourage investigators to view this
        method as a means of exploring their data for general temporal patterns
        of divergences across taxa, rather than a rigorous means of evaluating
        hypotheses.  As recommended by Oaks et al.\ \cite{Oaks2012}, any
        results from the method should be accompanied by (1) analyses under a
        variety of priors to assess the assumptions underlying model inference
        and the prior sensitivity of the results, and (2) simulation-based
        power analyses to provide insight into the temporal resolution of the
        method.  Both approaches are important to help guide the interpretation
        of results.
    \end{quote}
}

\revcomment{
    Reviewer 1 requested that we elaborate about how Robert et al's
    \cite{Robert2011} critique of ABC model choice relates to \dppmsbayes.
}
\response{
    I have expanded:
    \begin{quote}
        I also urge caution when using dpp-msbayes due to the fact that ABC
        methods in general are known to be biased for model choice
        \cite{Robert2011}.
    \end{quote}
    to:
    \begin{quote}
        I also urge caution when using \dppmsbayes due to the lack of
        theoretical validation of Bayesian model choice when the full data are
        replaced by summary statistics that are insufficient for discriminating
        across models under comparison \cite{Robert2011}, which is certainly
        the case here.  Robert et al.\ \cite{Robert2011} demonstrated that ABC
        estimates of model posterior probabilities can be inaccurate when such
        across-model insufficient statistics are used.
    \end{quote}
    I think this makes it more clear how the findings of \cite{Robert2011} are
    potentially relevant to the posterior probabilities estimated by
    \dppmsbayes and \msb.
}

@@

\section{Reviewer 2's Comments}
\setcounter{commentCounter}{0}

\revcomment{
    The complaint that ``This causes divergence models with more divergence-time
    parameters to integrate over a much greater parameter space with low
    likelihood yet high prior density, resulting in small marginal likelihoods
    relative to models with fewer divergence-time parameters.'' (p.2) is
    essentially stressing the point with Occam's razor argument. Which I deem a
    rather positive feature of Bayesian model choice. A reflection on the
    determination of the prior distribution away from uniform priors thus
    sounds most timely, rather than a criticism of the Bayesian foundations.
}
\response{
    Sorry for the confusion here. This statement was not intended as
    a general criticism of Bayesian foundations. Rather, the intent was to
    highlight why prior choice is very important in Bayesian model choice.
    I have added the following sentences to clarify:
    \begin{quote}
        This is not a critique of Bayesian model choice in general; comparing
        models by their marginal likelihoods provides a ``natural'' penalty for
        over-parameterization and can be a great strength of the Bayesian
        approach.  However, given the sensitivity of marginal likelihoods to
        the prior, care is needed when selecting prior distributions
        \cite{Lindley1957}.  Selecting distributions that will often place high
        prior density in large regions of parameter space with low likelihood
        can lead to small marginal likelihoods of parameter-rich models even if
        they are correct.
    \end{quote}
}

\revcomment{
    The current paper claims to have reached a satisfactory prior modelling
    with ``improved robustness, accuracy, and power'' (p.3). If I understand
    correctly, the changes are in replacing a uniform distribution with a Gamma
    or a Dirichlet prior.  Which means introducing a seriously large number of
    hyperparameters into the picture. Having a lot of flexibility in the prior
    also means a lot of variability in the resulting inference. This is a
    general feature of all Bayesian modellings and I am rather surprised by the
    conclusion that things look better by taking this step away from the
    uniform prior. Depending on the problem they could also look worse.
}
\response{
    Both uniform and gamma distributions have two parameters. Thus, the new
    model only has one additional hyperparameter compared to the original
    msBayes model: the concentration parameter on the Dirichlet process prior
    on divergence models. Also, as described in the manuscript, the new method
    offers a uniform prior over divergence models, which would have the same
    number of hyper-parameters as the original method.

    Also, in both msBayes and dpp-msbayes the hyper-parameters are fixed, and
    thus do not contribute variability to the model. While a hiearchical
    approach that places hyper-priors on the various hyper-parameters would be
    interesting to explore for either the msBayes or dpp-msbayes model, it is
    beyond the scope of the current study.

    I have added some text to various places in the manuscript to clarify that
    the hyper-parameters are fixed rather than estimated:
    \begin{quote}
        If the recombination rate \recombinationRate is allowed to be non-zero,
        the prior term $p(\recombinationRate)$ would be added to Equation
        2, and the prior would be $\recombinationRate
        \sim Gamma(\gammaShape{\recombinationRate},
        \gammaScale{\recombinationRate})$, \change{where
        \gammaShape{\recombinationRate} and \gammaScale{\recombinationRate} are
        specified by the investigator.}
    \end{quote}

    \begin{quote}
        The priors for the demographic parameters are $\ancestralTheta{} \sim
        Gamma(\gammaShape{\ancestralTheta{}}, \gammaScale{\ancestralTheta{}})$,
        $\descendantTheta{1}{} \sim Gamma(\gammaShape{\descendantTheta{}{}},
        \gammaScale{\descendantTheta{}{}})$, $\descendantTheta{2}{} \sim
        Gamma(\gammaShape{\descendantTheta{}{}},
        \gammaScale{\descendantTheta{}{}})$, $\bottleScalar{1}{} \sim
        Beta(\betaA{\bottleScalar{}{}}, \betaB{\bottleScalar{}{}})$,
        $\bottleScalar{2}{} \sim Beta(\betaA{\bottleScalar{}{}},
        \betaB{\bottleScalar{}{}})$, $\bottleTime{} \sim U(0, 1)$, and
        $\migrationRate{} \sim Gamma(\gammaShape{\migrationRate{}},
        \gammaScale{\migrationRate{}})$, \change{where the hyper-parameters of
        each prior distribution can be specified by the investigator.  By
        default, \ancestralTheta{}, \descendantTheta{1}{}, and
        \descendantTheta{2}{} share the same prior (i.e.,
        $\gammaShape{\ancestralTheta{}} = \gammaShape{\descendantTheta{}{}}$
        and $\gammaScale{\ancestralTheta{}} =
        \gammaScale{\descendantTheta{}{}}$), but a separate gamma-distributed
        prior can be assigned to \ancestralTheta{}.  Also, the
        \bottleScalar{1}{}, \bottleScalar{2}{}, and \migrationRate{} parameters
        are optional (i.e., the investigator can assume that there has been no
        migration between populations of each pair and/or the population size
        of each descendant population has been constant through time).}
    \end{quote}

    \begin{quote}
        Each \divTime{} within \divTimeVector is \iid as $\divTime{} \sim
        Gamma(\gammaShape{\divTime{}}, \gammaScale{\divTime{}})$, \change{
        where \gammaShape{\divTime{}} and \gammaScale{\divTime{}} are specified
        by the investigator}.
    \end{quote}
}

\revcomment{
    The ABC part is rather standard, except for the rather strange feature that
    the divergence times are used to construct summary statistics (p.10). I
    find it strange because these times are not observed for the actual data.
    So I must be missing something, which should be spelled out more clearly.
    (And I object to the sentence ``I have introduced a new approximate-Bayesian
    model choice method.'' (p.21) since there is no new ABC technique, simply a
    different form of prior.)
}
\response{
    Reviewer 2 is correct that there is no new ABC numerical machinery
    presented in the manuscript, only a new model. To make this clearer,
    I have changed the sentence to:
    \begin{quote}
        I introduced a new model for estimating shared divergence histories
        across taxa from DNA sequence data within an approximate-Bayesian
        model-choice framework.
    \end{quote}

    Also, the intuition of Reviewer 2 is correct, I do not use the divergence
    times to calculate summary statistics. I mention the divergence times in
    the description of the ABC algorithm with the hope of making it clear that
    the times are scaled (see Equation (12)) prior to the simulation of the
    data (from which the summary statistics are calculated). This scaling is
    simply to go from units proportional to time, to units that are
    proportional to the expected number of mutations. Because, this is already
    described earlier in the description of the model, I have removed the
    re-description of this scaling from the description of the ABC algorithm.

    This section now reads as:

    \begin{quote}
        Each sample is generated by \change{(1) drawing values of all the
            model's parameters, which I denote \hpvector{}, from their
            respective prior distributions; (2) simulating gene trees
            $\geneTreeVector = (\geneTree{1}{1}, \ldots,
            \geneTree{\npairs{}}{\nloci{\npairs{}}})$ for each locus of each
            population pair by drawing coalescent times from a multi-population
            Kingman-coalescent model given the demographic parameters; (3)
            simulating sequence alignments $\alignmentVector =
            (\alignment{1}{1}, \ldots,
            \alignment{\npairs{}}{\nloci{\npairs{}}})$ along the gene trees
            under the \hky substitution parameters $\hkyModelVector =
            (\hkyModel{1}{1}, \ldots, \hkyModel{\npairs{}}{\nloci{\npairs{}}})$
            that have the same number of sequences and sequence lengths as the
            observed dataset; and (4) calculating population genetic summary
            statistics $\ssVector{} = (\alignmentSS{1}{1}, \ldots,
            \alignmentSS{\npairs{}}{\nloci{\npairs{}}})$ from the simulated
        sequence alignments.}
    \end{quote}

    Many thanks to Reviewer 2 for catching this potential source of confusion.
}

\revcomment{
    I do not understand much the part about (reshuffling) introducing bias as
    detailed on p.11: every approximate method gives a ``biased'' answer in the
    sense this answer is not the true and proper posterior distribution. Using
    a different (re-ordered) vector of statistics provides a different ABC
    outcome, hence a different approximate posterior, for which it seems truly
    impossible to check whether or not it increases the discrepancy from the
    true posterior, compared with the other version. I always find it annoying
    to see the word `bias' used in a vague meaning and esp. within a Bayesian
    setting. All Bayesian methods are biased.
}
\response{
    Regarding the reshuffling of the summary statistics calculated from
    different alignments of sequences, those statistics are not exchangeable.
    So, reshuffling them in a manner that is not consistent across all
    simulations and the observed data (as is done in msBayes) is not
    mathematically valid. Also, if elements are exchangeable, their order will
    not affect the likelihood (or the posterior). Thus, if the goal is to
    approximate the likelihood, the reshuffling should also have little affect
    on the approximate posterior. The fact that \cite{Huang2011} demonstrate
    that it does strongly affect the posterior suggests this reshuffling is not
    only mathematically incorrect, but also is misleading the results.

    I have revised this section to make it more precise and clear:
    \begin{quote}
        \change{
        The re-ordering of the summary statistic vectors also has an important
        implication for the ABC algorithm.  When calculating the Euclidean
        distance between the observed data and each simulated dataset, the
        summary statistics being compared often represent sequence alignments
        of \emph{different} taxon pairs and/or loci.  More specifically, the
        summary statistics calculated from the observed sequence alignments are
        being compared to summary statistics calculated from datasets simulated
        with potentially \emph{different} (1) numbers of sequences
        (\popSampleSize{1}{} and \popSampleSize{2}{}), (2) length of
        alignments, (3) numbers of loci (\nloci{}), (4) \hky model parameters
        (\hkyModel{}{}), (5) mutation-rate multipliers
        (\mutationRateScalarConstant{}{}), and (6) ploidy multipliers
        (\ploidyScalar{}{}).}

### 2014-06-01 manuscripts/dpp-msbayes/reviews/response.tex

        In the original descriptions of the \msb method
        \cite{Hickerson2006,Huang2011}, this re-ordering is justified by the
        fact that the expected value of $\pi_b$ is unrelated to sample size
        \popSampleSize{1}{} and \popSampleSize{2}{} and thus exchangeable among
        pairs.  \change{ This is incorrect for two reasons.} First, the entire
        vector of summary statistics \alignmentSS{}{} for each pair of
        populations is re-ordered across pairs, which implies that the
        justification for re-ordering $\pi_b$ applies to all the statistics
        within each \alignmentSS{}{}.  \change{However, the expectations for
        statistics that estimate gross diversity (e.g., $\pi$ and $\theta_W$)
        are not independent of sample size for structured populations (e.g.,
        the divergent pairs of populations modeled by \msb), and other
        statistics are not independent of sample size in general (e.g.,
        $SD(\pi-\theta_W)$).  Second, and more importantly, having the same
        expectation does not ensure random variables are exchangeable.  Rather,
        for variables to be exchangeable their marginal distributions must be
        the same (i.e., they must be identically distributed).  None of the
        summary statistics used by \msb, including $\pi_b$, are identically
        distributed when there is any variation among taxa or loci in the (1)
        numbers of sequences (\popSampleSize{1}{} and \popSampleSize{2}{}), (2)
        length of alignments, (3) numbers of loci (\nloci{}), (4) \hky model
        parameters (\hkyModel{}{}), (5) mutation-rate multipliers
        (\mutationRateScalarConstant{}{}), or (6) ploidy multipliers
        (\ploidyScalar{}{}).  Whenever such variation is present (i.e., nearly
        all empirical applications), the taxon-specific summary statistics
        \alignmentSS{}{} are not exchangeable, and the reshuffling of the
        summary statistic vectors is not mathematically valid.

        The magnitude of the affect of this violation of exchangeability is not
        known.  Huang et al.\ \cite{Huang2011} demonstrated that the reordering
        of the summary statistic vectors can greatly increase the method's
        tendency to infer a single divergence event.  By definition, if the
        summary statistic vectors were exchangeable, the reordering would not
        change the likelihood or posterior (barring sampling error).  Thus, the
        results of Huang et al.\ \cite{Huang2011} suggest the reordering of the
        statistics is potentially introducing sizeable error to the analysis.}
    \end{quote}
}

\revcomment{
    Quoting [43] as concluding that ABC model choice is biased is
    somewhat misleading: the warning therein was that Bayes factors and
    posterior probabilities resulting from those ABC steps could be quite
    unrelated with those based on the whole dataset. That the same authors
    concluded that the proper choice of summary statistics leads to a
    consistent model choice shows ABC model choice is not necessarily
    ``biased''.
}
\response{
    This is a very good point, thank you. I have expanded this section to be
    clearer about the findings of \cite{Robert2011} and how they relate to the
    methods discussed in the paper:
    \begin{quote}
        I also urge caution when using \dppmsbayes due to the lack of
        theoretical validation of Bayesian model choice when the full data are
        replaced by summary statistics that are insufficient for discriminating
        across models under comparison \cite{Robert2011}, which is certainly
        the case here.  Robert et al.\ \cite{Robert2011} demonstrated that ABC
        estimates of model posterior probabilities can be inaccurate when such
        across-model insufficient statistics are used.
    \end{quote}
}

\revcomment{
    I also fail to understand why the posterior probability of model i should
    be distributed as a uniform (``If the method is unbiased, the points should
    fall near the identity line'') when the data is from model i: this is not a
    p-value but a posterior probability and the posterior probability is not
    the frequentist coverage.
}
\response{
    I agree that the justification of why the identity line should be
    considered ``unbiased'' was too vague and relied entirely on the reference
    to \cite{Huelsenbeck2004}. I have expanded this section to be very explicit
    what is meant by ``bias'' and why it is desirable for the method to produce
    estimates that fall along the identity line:
    \begin{quote}
        Ideally, the estimated posterior probability of the one-divergence
        model should estimate the probability that the one-divergence model is
        correct.  For large numbers of simulation replicates, the proportion of
        the replicates in each bin for which the one-divergence model is true
        will approximate the probability that the one-divergence model is the
        correct model.  Thus, if the method has the desirable behavior such
        that the estimated posterior probability of the one-divergence model is
        an unbiased estimate of the probability that the one-divergence model
        is correct, the points should fall near the identity line.  For
        example, let us say the method estimates a posterior probability of
        0.90 for 1000 datasets simulated from the prior.  If the method is
        accurately estimating the probability that the one-divergence model is
        correct given the data, then the one-divergence model should be the
        true model in approximately 900 of the 1000 replicates.  Any trend away
        from the identity line indicates the method is biased in the sense that
        it is not accurately estimating the probability that the one-divergence
        model is the correct model.
    \end{quote}
}

\revcomment{
    My overall problem with the paper is that, all in all, this is a single
    Monte Carlo study about the performances of some classes of priors and, as
    such, it does not carry enough weight to validate an approach that remains
    highly subjective in the selection of its hyperparameters. I think this
    remains a controlled experiment with simulated data where the true
    parameters are know and the prior is ``true''. This obviously helps in
    getting better performances. In a different and less controlled experiment,
    a new experimenter may (should?) be at a loss as to which hyperparameters
    to chose.
}
\response{
    I agree. However, the goal of the paper is not to demonstrate, for example,
    that gamma probability distributions are generally superior to uniform
    probability distributions for Bayesian model-choice. Nor is the goal to
    solve the subjective nature of prior selection in Bayesian statistics.
    My primary goal was to develop an improved comparative method that
    biogeographers can use to investigate the affect of historical events on
    diversification.

    I used extensive simulations and biological data to compare, as fairly as
    possible, the new approach to the current state-of-the-art method for this
    inference problem. I agree the new approach has many weaknesses, including
    the subjective nature of choosing priors when the truth is unknown.
    However, these weaknesses apply to \emph{both} \dppmsbayes and \msb
    (and to all empirical applications of Bayesian statistical methods where
    extensive prior information is lacking). However, the results strongly
    support the overall conclusion that the primary goal was accomplished, and
    the new approach outperforms \msb under a range of conditions.
}

\revcomment{
    The conclusion of the paper that ``With improving numerical methods (...),
    advances in Monte Carlo techniques and increasing efficiency of likelihood
    calculations, analyzing rich comparative phylo-geographical models in a
    full-likelihood Bayesian framework is becoming computationally feasible.''
    (p.21) sounds overly optimistic and rather premature. As to this day, I do
    not know of any significant advance in computing the observed likelihood
    for the population genetics models ABC is currently handling. (The SMC
    algorithm of Bouchard-C\^{o}t\'{e}, Sankaraman and Jordan 2012 does not apply to
    Kingman's coalescent, as far as I can judge.) This is certainly a goal
    worth pursuing and borrowing strength from multiple techniques cannot hurt,
    but it remains so far a lofty goal, still beyond our reach... I thus think
    the major message of the paper is to reinforce our earlier calls for
    caution when interpreting the output of an ABC model choice (p.20), or even
    of a regular Bayesian analysis, agreeing that we should aim at seeing ``a
    large amount of posterior uncertainty'' rather than posterior probability
    values close to 0 and 1.
}
\response{
    Full-likelihood methods in this domain are not as lofty of a goal as you
    might think. The likelihood function of the msBayes model is tractable,
    and, in fact, has already been derived and implemented via reversible-jump
    MCMC (see \cite{JeetDiss}; albeit, not readily available yet).
    Also, there are plenty of examples of rich, Kingman-coalescent models
    implemented in a full-likelihood Bayesian framework.
    A small sample includes \cite{Drummond2005,Drummond2008,Drummond2002,Kuhner1995,Hey2007,Hey2010,Bryant2012,Shapiro2011,Vaughan2014,Heled2010,Lemey2009,Lemey2010,Pybus2012,Baele2012,Minin2008beast,Bloomquist2010}.
    Also, the SMC algorithm of \cite{Jordan2012} can be used to estimate
    phylogenetic trees using an arbitrary prior on trees (e.g., Birth-death
    process, coalescent, etc.).
}

### 2014-06-01 manuscripts/dpp-msbayes/dpp-msbayes-acknowledgments.tex
Working on dpp ms revisions.

I am greatful to Melissa Callahan, Mark Holder, Emily McTavish, Daniel Money,
Jordan Koch, and Adam Leach\'{e} for insightful comments that greatly improved
this work.
I thank the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
This work was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
I also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.

>>>>

\change{
I am greatful to Melissa Callahan, Mark Holder, Emily McTavish, Daniel Money,
Jordan Koch, Adam Leach\'{e}, Peter Foster, two anonymous reviewers, and
Christian Robert and his blog
(\href{http://xianblog.wordpress.com/}{\url{http://xianblog.wordpress.com/}})
for insightful comments that greatly improved this work.
}
I thank the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
This work was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
I also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.
